---
title: "Paper 1 [working title]"
author: 
  - Winny Peng
thanks: "Code and data are available at: https://github.com/pengwinny/starter_folder."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "In Toronto, before a neighbourhood change application can be processed for consideration, the city must first consult the opinions of property owners, residents and businesses from the affected area via polls. Regardless of whether changes are good or bad, it is important to know which types of neighbourhood modifications resident stakeholders are most resistant to. In this particular analysis, we gathered polling data from the City of Toronto Open Portal to examine which types of neighbourhood change receive lower response rates. Interestingly enough, it appears that Torontonians are very passionate about parking but less eager about traffic changes."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

# Introduction

First paragraph is first sentence from abstract but add more water.

Second paragraph is about what was done and what was found.

Third paragraph is about implications (final sentence but add water)

The remainder of this paper is: Section \@ref(data) explains the data. Section \@ref(results) covers results ...


# Data

Paragraph or two introducing the data set broadly. We obtain our data set from the City of Toronto open Data Portal, using the `opentorontodata` package [@citeopendatatoronto] and the statistical programming language R [@citeR].

Then show an extract of the data set (Table \@ref(tab:dataextract).

```{r dataextract, echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(knitr)

toronto_poll_data <- read_csv(here::here("inputs/data/toronto_poll_data.csv"))

toronto_poll_data |> 
  select(RESPONSE_RATE_MET, APPLICATION_FOR,) |> 
  slice(1:10) |> 
  kable(
    caption = "First ten rows of a dataset of economic indicators for 
    Australia, Ethiopia, India, and the US",
    col.names = c("Response Rate Met", "Poll Type"),
    digits = 1,
    booktabs = TRUE,
    linesep = ""
  )
```

Paragraph or two more about Table.

We are interested in the relationship between A and B.

```{r bargraph, echo=FALSE}
toronto_poll_data |> 
  ggplot(mapping = aes(y = APPLICATION_FOR, fill = RESPONSE_RATE_MET)) +
  geom_bar(position = "dodge") +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(x = "Number of times response rate is met",
       y = "Application type",
       fill = "Response Rate Met",
       title = "Application types and their response rates.") +
  theme_classic()
```

Figure X shows the relationship between Y and Z.

```{r bargraph, echo=FALSE}
toronto_poll_data |> 
  ggplot(mapping = aes(y = APPLICATION_FOR, fill = POLL_RESULT)) +
  geom_bar(position = "dodge") +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(x = "Number of times response rate is met",
       y = "Application type",
       fill = "Response Rate Met",
       title = "Application types and their response rates.") +
  theme_classic()
```

Talk more about it.

Also bills and their average. (Notice how you can change the height and width so they don't take the whole page?)

Talk way more about it. 

# Results

\appendix

# Appendix {-}


# Additional details


\newpage


# References


