---
title: "Paper 1 [working title]"
author: 
  - Winny Peng
thanks: "Code and data are available at: https://github.com/pengwinny/starter_folder."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence is super broad and motivational. Second sentence is more specific on what I did. Third sentence. Fourth sentence is something about our findings."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

# Introduction

First paragraph is first sentence from abstract but add more water.

Second paragraph is about what was done and what was found.

Third paragraph is about implications (final sentence but add water)

The remainder of this paper is: Section \@ref(data) explains the data. Section \@ref(results) covers results ...


# Data

Paragraph or two introducing the data set broadly. We obtain our data set from the City of Toronto open Data Portal, using the `opentorontodata` package [@citeopendatatoronto] and the statistical programming language R [@citeR].

Then show an extract of the data set (Table \@ref(tab:dataextract).

```{r dataextract, echo=FALSE}
library(tidyverse)
library(knitr)

toronto_poll_data <- read_csv(here::here("inputs/data/toronto_poll_data.csv"))

toronto_poll_data |> 
  select(POLL_RESULT, RESPONSE_RATE_MET,) |> 
  slice(1:10) |> 
  kable(
    show_col_types = FALSE,
    caption = "First ten rows of a dataset of economic indicators for 
    Australia, Ethiopia, India, and the US",
    col.names = c("Poll Result", "Response Rate"),
    digits = 1,
    booktabs = TRUE,
    linesep = ""
  )
```

Paragraph or two more about Table.

We are interested in the relationship between A and B.

```{r bargraph, echo=FALSE}
toronto_poll_data |> 
  ggplot(mapping = aes(x = BALLOTS_NEEDED_TO_PROCEED, fill = POLL_RESULT)) +
  geom_bar() +
  theme_classic()
```

Figure X shows the relationship between Y and Z.

Talk more about it.

Also bills and their average. (Notice how you can change the height and width so they don't take the whole page?)

# {r billssssss, fig.cap="More bills of penguins", echo = FALSE, fig.width=8, fig.height=4}

Talk way more about it. 



# Model

\begin{equation}
Pr(\theta | y) = \frac{Pr(y | \theta) Pr(\theta)}{Pr(y)}  (\#eq:bayes)
\end{equation}

Equation \@ref(eq:bayes) seems useful, eh?

We can use maths by including latex between dollar signs, for instance $\theta$.


# Results

\appendix

# Appendix {-}


# Additional details


\newpage


# References


