---
title: "Paper 1 [working title]"
author: 
  - Winny Peng
thanks: "Code and data are available at: https://github.com/pengwinny/starter_folder."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence is super broad and motivational. Second sentence is more specific on what I did. Third sentence. Fourth sentence is something about our findings."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(palmerpenguins)
```

# Introduction

First paragraph is first sentence from abstract but add more water.

Second paragraph is about what was done and what was found.

Third paragraph is about implications (final sentence but add water)

The remainder of this paper is: Section \@ref(data) explains the data. Section /a@ref(results) covers results ...



# Data

Paragraph or two introducing the dataset broadly.

Then show an extract of the dataset (Table /@ref(tab:dataextract).

```{r dataextract}
library(tidyverse)
library(knitr)

toronto_poll_data <- read_csv(here::here("inputs/data/toronto_poll_data.csv"))

toronto_poll_data |> 
  select(POLL_RESULT, RESPONSE_RATE_MET) |> 
  slice(1:10) |> 
  kable(
    caption = "First ten rows of a dataset of economic indicators for 
    Australia, Ethiopia, India, and the US",
    col.names = c("Poll Result", "Response Rate"),
    digits = 1,
    booktabs = TRUE,
    linesep = ""
  )
```

Paragraph or two more about Table.



Our data is of penguins (Figure \@ref(fig:bills)).

```{r bills, fig.cap="Bills of penguins", echo = FALSE}
ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = FALSE) +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

Also bills and their average (Figure \@ref(fig:billssssss)). (Notice how you can change the height and width so they don't take the whole page?)

```{r billssssss, fig.cap="More bills of penguins", echo = FALSE, fig.width=8, fig.height=4}

# This needs to be about the random data tha tI sasmpled?
ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = FALSE) +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk way more about it. 



# Model

\begin{equation}
Pr(\theta | y) = \frac{Pr(y | \theta) Pr(\theta)}{Pr(y)}  (\#eq:bayes)
\end{equation}

Equation \@ref(eq:bayes) seems useful, eh?

Here's a dumb example of how to use some references: In paper we run our analysis in `R` [@citeR]. We also use the `tidyverse` which was written by @thereferencecanbewhatever If we were interested in baseball data then @citeLahman could be useful. 

We can use maths by including latex between dollar signs, for instance $\theta$.


# Results

# Discussion

## First discussion point

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}


# Additional details


\newpage


# References


